Rapid, (semi-?)Supervised Generation of Novel Percussive Sounds with a Tractable Virtual Synthesizer

### 2020-01-13 paper.tex
Updates from Overleaf

% --- Author Metadata here. See Template---
\conferenceinfo{NIME'20,}{July 21-25, 2020, Royal Birmingham Conservatoire, ~~~~~~~~~~~~ Birmingham City University, Birmingham, United Kingdom.}
\title{Rapid, (semi-?)Supervised Generation of Novel Percussive Sounds With A Tractable Virtual Synthesizer}

@@

\todo[inline, color=green!30]{is this the right place to show off some t-sne graphs of how various feature extraction methods seperated drum categories?}

@@

\section{Novel Generations}
\label{gens}
\subsection{The Goal}
 Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category. We evaluate each method by measuring how many samples of categories \textit{kick,snare} and \textit{hat} can be produced in under a minute. Finally we show results of a survey conducted to measure the quality of these samples. 
\subsection{General Methods}
\colorbox{green!=30}{The next 3 sections will be modified heavily after the ear is updated.}
\subsubsection{Random Generation}
To establish a benchmark, we seek to establish the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters. We have observed a bias in generations as indicated in figure \ref{gens}.\\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-a}
\includegraphics[width=0.48\linewidth]{example-image-a}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
\label{fig:rand-graphs}
\end{figure}
\subsubsection{Multivariate Distribution Sampling}
Some success and extremely fast and scalable once the parameter space is calculated. A well known issue with this apporach is that the parameter space for virtual synthesizers are often neither differenciable nor gaussian \cite{esling2019universal} (a couple more papers also talked about this, I have to find them). Currently our parameters are array indices mapping to different values for Synth components. This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors. \\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-b}
\includegraphics[width=0.48\linewidth]{example-image-b}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
\label{fig:multi-graphs}
\end{figure}

\subsubsection{Evolutionary Search}
Implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}. A parameter set is assumed to be an individual with each parameter being its genes. To measure an individuals fitness, we use the formula $fitness=score-rank$. As generations evolve, a Hall-of-Fame list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
To ensure diversity of the HOF individuals, the fitness score should also consider some measure of uniqueness. A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
A generation of $N$ individuals are initialized(randomly or using already existing ranked parameters). To create the offspring generation, each generation goes through mutations and in-place gene crossovers. The new generation consists of the top 80\% of the offspring generation and 20\% new individuals to quicken gene diversity. If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.\\

>>>>

% --- Author Metadata here. See Template---
\conferenceinfo{NIME'20,}{July 21-25, 2020, Royal Birmingham Conservatoire, ~~~~~~~~~~~~ Birmingham City University, Birmingham, United Kingdom.}
\title{Rapid, (semi-?)Supervised Generation of Novel Percussive Sounds with a Tractable Virtual Synthesizer}

@@

\todo[inline, color=green!30]{is this the right place to show off some t-sne graphs of how various feature extraction methods separated drum categories? Or take the probability vector assigned to samples by the ear and t-sne that? it might be a cool way to visualize show how well the ear is performing}

@@

\section{Novel Generations}
\label{gens}
\subsection{The Goal}
 Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category. We evaluate each method by measuring how many samples of categories \textit{kick,snare} and \textit{hat} can be produced in under a minute. Finally we show results of a survey conducted to measure the quality of these samples. 
\subsection{General Methods}
\colorbox{green!=30}{The next 3 sections will be modified heavily after the ear is updated.}
\subsubsection{Random Generation}
To establish a benchmark, we seek to establish the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters. We have observed a bias in generations as indicated in figure \ref{gens}.\\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-a}
\includegraphics[width=0.48\linewidth]{example-image-a}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
\label{fig:rand-graphs}
\end{figure}
\subsubsection{Multivariate Distribution Sampling}
\colorbox{green!=40}{go over the math quick}\\
\colorbox{green!=40}{add some graphs showing learned params}\\
\colorbox{green!=40}{add graphs of learned parameters showing why it's not perfect}\\
This method is extremely fast and scalable once the parameter space is calculated. But success is limited due to well known issues with this approach. Notably that the parameter space for virtual synthesizers are often neither differentiable nor Gaussian. \cite{esling2019universal} (a couple more papers also talked about this, \colorbox{green!=40}{I have to look them up}). Currently our parameters are array indices mapping to different values for Synth components. This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors. \\
\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-b}
\includegraphics[width=0.48\linewidth]{example-image-b}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosen categories in under a minute}
\label{fig:multi-graphs}
\end{figure}

\subsubsection{Evolutionary Search}
We implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}. A parameter set is assumed to be an individual with each parameter being its genes. To measure an individuals fitness, we use the formula $fitness=score-rank$. As generations evolve, a Hall-of-Fame list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
To ensure diversity of the HOF individuals, the fitness score should also consider some measure of uniqueness. A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
A generation of $N$ individuals are initialized(randomly or using already existing ranked parameters). To create the offspring generation, each generation goes through mutations and in-place gene crossovers. The new generation consists of the top 80\% of the offspring generation and 20\% new individuals to quicken gene diversity. If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.\\
